cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added initial projection for linear data

>>>>

```{r data-linear, echo=TRUE}
linear <- gen_longlinear(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(linear)
```

```{r linear-proj1}
scaled_data <- scale_data_manual(linear)

linear_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r linear-proj2}

linear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r linear-proj3}

linear_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-linear-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linear` data."}
#| fig-width: 15
#| fig-height: 5

linear_proj1 + linear_proj2 + linear_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
